Title Goes Here

### 2019-04-22 analysis/paper/paper.Rmd
undates

```{r read-in-the-data}
library(here)
kwl_upper <- readxl::read_excel(here("analysis", "data", "raw_data", "Kiwulan_Ornament_Upper.xlsx"))
```

@@

```{r tidy-data}
# summarise the ornaments by layers
library(tidyverse)
library(ggplot2)

@@

```{r scatter-plot-bead-by-period}

# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Golden bead')

@@

```{r read-in-the-spatial-data}
library(sf)
library(cartography)
burial <- st_read(here("analysis", "data", "raw_data", "AD_burial.shp"))
AD <- st_read(here("analysis", "data", "raw_data", "AD_zone.shp"))
AD_data <- st_read(here("analysis", "data", "raw_data", "AD_withdata.shp"))
location <- st_read(here("analysis", "data", "raw_data", "location.shp"))
units_40 <- read.csv(here("analysis", "data", "raw_data", "kwl-list-of-sampling-squares.csv"))
```

```{r tidy-data2}
# 40 sampling units
sample_units <-
  AD_data %>% 
  semi_join(units_40, by = c (`坑號` = "the_sq"))

>>>>

```{r read-in-the-data, eval = TRUE}
library(here)
kwl_upper <- readxl::read_excel(here("analysis", "data", "raw_data", "Kiwulan_Ornament_Upper.xlsx"))
```

@@

```{r tidy-data, eval = TRUE}
# summarise the ornaments by layers
library(tidyverse)
library(ggplot2)

@@

```{r scatter-plot-bead-by-period}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Golden bead')

@@

```{r read-in-the-spatial-data, eval = TRUE}
library(sf)
library(cartography)
burial <- st_read(here("analysis", "data", "raw_data", "AD_burial.shp"))
AD <- st_read(here("analysis", "data", "raw_data", "AD_zone.shp"))
AD_data <- st_read(here("analysis", "data", "raw_data", "AD_withdata.shp"))
location <- st_read(here("analysis", "data", "raw_data", "location.shp"))
units_40 <- read.csv(here("analysis", "data", "raw_data", "kwl-list-of-sampling-squares.csv"))
```

```{r tidy-data2, eval = TRUE}
# 40 sampling units
sample_units <-
  AD_data %>% 
  semi_join(units_40, by = c (`坑號` = "the_sq"))
